### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Added peak shift table for dynamic XRD. Meant to make one for annealing XRD...
Suplimentary - Added annealing XRD peak list table. Cannot go in main body like I though.

@@

@@

>>>>

\begin{table}[h]
	\centering
	\caption{Location of the bulk and film peaks for the dynamic \acrshort{xrd} Mg, \MgZn, and \CaMgZnFive~ compounds.}
	\begin{tabular}{ c c c c c c c c c }
		\toprule
		\multicolumn{3}{c}{Mg} & \multicolumn{3}{c}{\MgZn} & \multicolumn{3}{c}{\CaMgZnFive} \\
		Bulk & Film & Change \% & Bulk & Film & Change \% & Bulk & Film & Change \% \\
		\midrule
		32.1 & 32.1 & 0.0\%  & 32.1 & 32.1   & 0.0\%  & 34.1 & 34.1 & 0.0\% \\
		34.3 & 34.3 & 0.0\%  & 34.3 & 34.3   & 0.0\%  & 34.6 & 35.1 & 1.4\% \\
		36.6 & 36.5 & -0.3\% & 36.6 & 36.5   & -0.3\% & 36.0 & 35.7 & -0.8\% \\
		47.7 & 47.6 & -0.2\% & 38.0 & 38.2   & 0.5\%  & 38.0 & 38.2 & 0.5\% \\
		57.2 & 57.1 & -0.2\% & 39.1 & 39.5   & 1.0\%  & 42.3 & 42.2 & -0.2\% \\
		&    &      & 45.1   & 45.2 & 0.2\%  & 43.7   & 43.3 & -0.9\% \\
		&    &      & 47.7   & 47.6 & -0.2\% & 53.3   & 53.0 & -0.6\% \\
		&    &      & 53.3   & 53.0 & -0.6\% &        &      &        \\
		&    &      & 57.2   & 57.1 & -0.2\% &        &      &        \\
		\bottomrule
	\end{tabular}
	\label{tab:Annealing_XRD_PeakShift}
\end{table}

@@

%Supplementary

@@

\begin{table}[b]
	\centering
	\caption{Supplementary: Annealing \acrshort{xrd} peak pattern list. Peaks which appear in both the bulk and film are marked "Both," peaks only appearing on the bulk are marked "Bulk Only," and peaks only appearing on the film are marked "Film Only."}
	\begin{tabular}{cccccccccc}
		\toprule
		\multicolumn{2}{c}{Mg} & \multicolumn{2}{c}{\MgZn} & \multicolumn{2}{c}{\CaMgZnFive} & \multicolumn{2}{c}{\CaMgZnThirteen} & \multicolumn{2}{c}{MgZn} \\
		\midrule
		32.264 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.636 & Both \\
		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.752 & Both \\
		36.7065 & Both & 19.429 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
		47.925 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.58 & Both \\
		63.2 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
		67.4268 & Both & 27.668 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
		68.7541 & Both & 30.4946 & Bulk Only & 30.3272 & Both & 27.947 & Both & 33.797 & Both \\
		70.121 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
		72.6686 & Both & 34.0114 & Both & 34.2311 & Both & 30.699 & Both & 35.892 & Both \\
		77.9616 & Both & 36.3948 & Both & 34.9708 & Bulk Only & 31.589 & Both & 37.121 & Both \\
		81.7143 & Both & 36.9487 & Bulk Only & 36.3289 & Both & 33.929 & Both & 38.101 & Both \\
		&  & 37.8181 & Both & 37.6976 & Both & 35.308 & Both & 39.312 & Both \\
		&  & 39.1701 & Both & 38.1445 & Both & 35.892 & Bulk Only & 40.416 & Both \\
		&  & 42.4369 & Both & 39.7631 & Both & 36.806 & Both & 41.989 & Both \\
		&  & 43.2937 & Both & 41.2057 & Both & 37.281 & Both & 42.824 & Both \\
		&  & 44.8168 & Both & 42.441 & Both & 38.269 & Both & 43.917 & Both \\
		&  & 47.9318 & Both & 43.9276 & Both & 40.041 & Both & 47.046 & Both \\
		&  & 57.4692 & Both & 45.3071 & Both & 40.991 & Both & 48.376 & Both \\
		&  & 63.2267 & Both & 48.1674 & Both & 42.195 & Both & 49.498 & Both \\
		&  & 64.1349 & Film Only & 52.0808 & Both & 43.038 & Both & 51.285 & Both \\
		&  & 65.0419 & Bulk Only & 53.6599 & Both & 43.917 & Both & 53.211 & Both \\
		&  & 65.3533 & Film Only & 56.9387 & Both & 44.6 & Both & 55.66 & Both \\
		&  & 68.5726 & Bulk Only & 58.561 & Both & 45.306 & Both & 57.955 & Both \\
		&  & 70.0382 & Both & 60.5081 & Both & 46.535 & Both & 60.026 & Both \\
		&  & 72.6234 & Both & 61.853 & Both & 47.306 & Film Only & 62.26 & Both \\
		&  & 76.4763 & Bulk Only & 62.9999 & Both & 48.104 & Bulk Only & 63.687 & Both \\
		&  & 77.2025 & Bulk Only & 64.3501 & Both & 50.079 & Both & 65.186 & Both \\
		&  & 78.3347 & Both & 65.632 & Both & 51.285 & Both &  &  \\
		&  & 82.0596 & Both & 66.831 & Both & 56.178 & Bulk Only &  &  \\
		&  &  &  & 68.7827 & Both & 58.601 & Both &  &  \\
		&  &  &  & 70.1095 & Both & 59.94 & Both &  &  \\
		&  &  &  & 71.8163 & Both & 62.028 & Both &  &  \\
		&  &  &  & 72.8322 & Bulk Only & 63.59 & Both &  &  \\
		&  &  &  & 74.9981 & Both & 64.427 & Both &  &  \\
		&  &  &  & 78.083 & Both & 66.229 & Both &  &  \\
		&  &  &  & 81.5094 & Bulk Only & 67.362 & Both &  &  \\
		&  &  &  & 82.6818 & Film Only & 68.198 & Both &  &  \\
		&  &  &  & 83.1204 & Both & 69.524 & Both &  &  \\
		&  &  &  &  &  & 70.48 & Both &  &  \\
		&  &  &  &  &  & 72.032 & Bulk Only &  &  \\
		&  &  &  &  &  & 73.329 & Both &  &  \\
		&  &  &  &  &  & 73.997 & Bulk Only &  &  \\
		&  &  &  &  &  & 76.736 & Both &  &  \\
		&  &  &  &  &  & 78.69 & Both &  &  \\
		&  &  &  &  &  & 79.631 & Both &  & \\
		%\bottomrule
	\end{tabular}
	\label{tab:Sub_Annealing_XRD_Peaks}
\end{table}
